Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-26 VMCAI-revised-version/final.tex
up

We claim {\sc Structual existential halting} in reset-VASS is undecidable.  
This is based on the construction providng the undecidability of structural termination in Lossy counter machines and in reset-VASS~\cite{dufourd1998reset,mayr1998lossy}. Strictly speaking undecidability of
{\sc Structual existential halting} is not considered in
\cite{mayr1998lossy},
but 
the encoding of Minsky machines can be reused
since 
 {\sc Structual existential halting}
 is equivalent to
 structural termination in the case of deterministic Minsky machines and thus,
 is undecidable for Minsky machines in general.

>>>>

We claim {\sc Structual existential halting} in reset-VASS is undecidable.  
This is based on the construction providng the undecidability of structural termination in Lossy counter machines and in reset-VASS~\cite{dufourd1998reset,mayr1998lossy}. Strictly speaking undecidability of
{\sc Structual existential halting} is not considered in
\cite{mayr1998lossy},
but 
the encoding of Minsky machines can be reused
since 
 {\sc Structual existential halting}
 is equivalent to
 structural termination in the case of deterministic Minsky machines and is thus
 undecidable for Minsky machines in general.
